---
title: "Genotype_recode"
output: html_notebook
author: "Yuting Qiu"
date: "2019-10-2"
---

Description: this is used to change the code with a loop in R and do some basic quality control, set the possible error sequnecing error in the marker as NA.


```{r}
#read in data
library(readxl)
D38 <- read_excel("geno_rqtl.xlsx", sheet = "D38_F")
D58 <- read_excel("geno_rqtl.xlsx", sheet = "D58_F")
D68 <- read_excel("geno_rqtl.xlsx", sheet = "D68_F")
D78 <- read_excel("geno_rqtl.xlsx", sheet = "D78_F")
```


# it should work now

```{r}
# i is the number of column
# j is the number of row
# p[i,j] i is row, j is column

cross <- D38
cross_l <- length(names(cross)) #column number
for (i in 1:cross_l){
  if(as.vector(unlist(cross[1,i])) =="CC" | as.vector(unlist(cross[1,i])) =="GG" | as.vector(unlist(cross[1,i])) =="AA" | as.vector(unlist(cross[1,i])) =="GG") {
    cross[,i] <- gsub("AB","NA", cross[,i]);
    cross[,i] <- gsub("BB","NA", cross[,i])
  }
}

# write.csv(cross, "D68_modifiec.csv")
# Not verfied for BB, see later

cross <- D58
cross_l <- length(names(cross)) #column number
for (i in 1:cross_l){
  if(as.vector(unlist(cross[1,i])) =="CC" | as.vector(unlist(cross[1,i])) =="GG" | as.vector(unlist(cross[1,i])) =="AA" | as.vector(unlist(cross[1,i])) =="GG") {
    cross[,i] <- gsub("AB","NA", cross[,i]);
    cross[,i] <- gsub("BB","NA", cross[,i])
  }
}

# write.csv(cross, "D58_modifiec.csv")

cross <- D68
cross_l <- length(names(cross)) #column number
for (i in 1:cross_l){
  if(as.vector(unlist(cross[1,i])) =="CC" | as.vector(unlist(cross[1,i])) =="GG" | as.vector(unlist(cross[1,i])) =="AA" | as.vector(unlist(cross[1,i])) =="GG") {
    cross[,i] <- gsub("AB","NA", cross[,i]);
    cross[,i] <- gsub("BB","NA", cross[,i])
  }
}

# write.csv(cross, "D68_modifiec.csv")

cross <- D78
cross_l <- length(names(cross)) #column number
for (i in 1:cross_l){
  if(as.vector(unlist(cross[1,i])) =="CC" | as.vector(unlist(cross[1,i])) =="GG" | as.vector(unlist(cross[1,i])) =="AA" | as.vector(unlist(cross[1,i])) =="GG") {
    cross[,i] <- gsub("AB","NA", cross[,i]);
    cross[,i] <- gsub("BB","NA", cross[,i])
  }
}

# write.csv(cross, "D68_modifiec.csv")


```


# merge gonotype file and phenotype file to get the format that can be used in R QC
```{r}
D38_GENO <- read.csv("D38_modifiec.csv")
D58_GENO <- read.csv("D58_modifiec.csv")
D68_GENO <- read.csv("D68_modifiec.csv")
D78_GENO <- read.csv("D78_modifiec.csv")
library(readxl)
D38_P <- read_excel("pheno.xlsx", sheet = "DRIL38")
D58_P <- read_excel("pheno.xlsx", sheet = "DRIL58")
D68_P <- read_excel("pheno.xlsx", sheet = "DRIL68")
D78_P <- read_excel("pheno.xlsx", sheet = "DRIL78")

D38GP <- merge(D38_GENO, D38_P, by.x = "Public.Name", by.y = "Public Name", all.x = TRUE)
D58GP <- merge(D58_GENO, D58_P, by.x = "Public.Name", by.y = "Public Name", all.x = TRUE)
D68GP <- merge(D68_GENO, D68_P, by.x = "Public.Name", by.y = "Public Name", all.x = TRUE)
D78GP <- merge(D78_GENO, D78_P, by.x = "Public.Name", by.y = "Public Name", all.x = TRUE)

write.csv(D38GP, "D38GP.csv")
write.csv(D58GP, "D58GP.csv")
write.csv(D68GP, "D68GP.csv")
write.csv(D68GP, "D78GP.csv")
```

follow the book https://www.biostat.wisc.edu/sites/default/files/tr_214.pdf
and conduct QC



###############################################
######### QC ##################################
###############################################

```{r}
library(qtl)
DRIL38_GW <- read.cross("csv", dir = "C:/Users/yutingq2/Desktop/1819GossWilt/5. Joint-linkage_mapping/QC_in_R/QC_joint_linkage/QC_READY","D38GP_GW.csv", estimate.map = FALSE, genotypes=c("AA","BB","AB"), na.strings=c("-","NA"), crosstype = "f2") 
# with estimate being false, the markers will be assigned to dummy locations, with no attempt to estimate the inter-marker distances
summary(DRIL38_GW)

DRIL58_GW <- read.cross("csv", dir = "C:/Users/yutingq2/Desktop/1819GossWilt/5. Joint-linkage_mapping/QC_in_R/QC_joint_linkage/QC_READY","D58GP_GW.csv", estimate.map = FALSE, genotypes=c("AA","BB","AB"), na.strings=c("-","NA"), crosstype = "f2") 
summary(DRIL58_GW)

DRIL68_GW <- read.cross("csv", dir = "C:/Users/yutingq2/Desktop/1819GossWilt/5. Joint-linkage_mapping/QC_in_R/QC_joint_linkage/QC_READY","D68GP_GW.csv", estimate.map = FALSE, genotypes=c("AA","BB","AB"), na.strings=c("-","NA"), crosstype = "f2") 
summary(DRIL68_GW)

DRIL78_GW <- read.cross("csv", dir = "C:/Users/yutingq2/Desktop/1819GossWilt/5. Joint-linkage_mapping/QC_in_R/QC_joint_linkage/QC_READY","D78GP_GW.csv", estimate.map = FALSE, genotypes=c("AA","BB","AB"), na.strings=c("-","NA"), crosstype = "f2") 
summary(DRIL78_GW)


```

get the overall map about the genotype
```{r}
plot(DRIL38_GW)
plot(DRIL58_GW)
plot(DRIL68_GW)
plot(DRIL78_GW)

jittermap(DRIL38_GW)
jittermap(DRIL58_GW)
jittermap(DRIL68_GW)
jittermap(DRIL78_GW)
# overall, there are some missing, and several markers has a lot of missing data. 
```


# 1. omit individuals and markers with missing data
```{r}
plotMissing(DRIL38_GW)
plotMissing(DRIL58_GW)
plotMissing(DRIL68_GW)
plotMissing(DRIL78_GW)

# look at the number of markers for indiviuals and the number of genotype by individual
# to omit the individuals with a lot of missing data
# ntyped() is used to Count the number of genotypes for each individual or each marker in a cross.
par(mfrow=c(1,2), las=0)
plot(ntyped(DRIL38_GW, what = "ind"), ylab = "Num. of typed markers", main = "Num. of genotypes by individual")
plot(ntyped(DRIL38_GW, what = "mar"), ylab = "Num. of typed individuals", main = "Num. of individuals by marker")

par(mfrow=c(1,2), las = 0)
plot(ntyped(DRIL58_GW, what = "ind"), ylab = "Num. of typed markers", main = "Num. of genotypes by individual")
plot(ntyped(DRIL58_GW, what = "mar"), ylab = "Num. of typed individuals", main = "Num. of indiduals by marker")

par(mfrow=c(1,2), las=0)
plot(ntyped(DRIL68_GW, what = "ind"), ylab = "Num. of tyoed markers", main = "Num. of genotypes by invidual")
plot(ntyped(DRIL68_GW, what = "mar"), ylab = "Num. of typed individuals", main = "Num. of indiduals by marker")

par(mfrow=c(1,2), las=0)
plot(ntyped(DRIL78_GW, what = "ind"), ylab = "Num. of tyoed markers", main = "Num. of genotypes by invidual")
plot(ntyped(DRIL78_GW, what = "mar"), ylab = "Num. of typed individuals", main = "Num. of indiduals by marker")
```


```{r}
# either based on marker numbers or based on individual numbers

# omit the individual missing data, 650 as cutoff, subset is for row and select is for column
DRIL38_GW.1 <- subset(DRIL38_GW, ind = (ntyped(DRIL38_GW, "ind")>650)) #TURE OR false
DRIL58_GW.1 <- subset(DRIL58_GW, ind = (ntyped(DRIL58_GW, "ind")>620)) #TURE OR false
DRIL68_GW.1 <- subset(DRIL68_GW, ind = (ntyped(DRIL68_GW, "ind")>680)) #TURE OR false
DRIL78_GW.1 <- subset(DRIL78_GW, ind = (ntyped(DRIL78_GW, "ind")>600)) #TURE OR false

which(ntyped(DRIL38_GW, "ind")<650)
## [1]   9  10  31  35  45  59 126 161 191 192 193 194
which(ntyped(DRIL58_GW, "ind")<620)
## [1]  57  95  96  97  98  99 100 101 102
which(ntyped(DRIL68_GW, "ind")<680)
## [1] 7
which(ntyped(DRIL78_GW, "ind")<600)
## [1] 182

# omit the markers wih too much missing data , 140 as cutoff for DRIL38
todrop_mar38 <- names(nt.bymar[ntyped(DRIL38_GW, "mar") < 140])
## [1] "PZA00192.6" "PHM1505.31" "PZA00686.4"
todrop_mar58 <- names(nt.bymar[ntyped(DRIL58_GW, "mar") < 68])
## [1] "PZA00010.5" "PZA01779.1" "PHM4495.14"
todrop_mar68 <- NULL
todrop_mar78 <- names(nt.bymar[ntyped(DRIL78_GW, "mar") < 140])
##[1] "PHM793.25"  "PHM15251.5" "PHM15501.9"


```


prior to this, I delete all the lines and markers with too many NA and then I will do the sgregation analysis. 


#################################################
################ NEW POINT ######################
#################################################
```{r}
# now try to write a loop to conduct chi-square test in the segregation rate for the four DRIL population

## test to write a loop 
### IT WORKS! :)#####################################################################################
library(readxl)
sgobs38 <- read_excel("QC_READY/segratio_obs_1.xlsx", sheet = "D38")
sgobs58 <- read_excel("QC_READY/segratio_obs_1.xlsx",  sheet = "D58")
sgobs68 <- read_excel("QC_READY/segratio_obs_1.xlsx",  sheet = "D68")
sgobs78 <- read_excel("QC_READY/segratio_obs_1.xlsx",  sheet = "D78")


to_num <- function(x) {
  for (i in 2:ncol(x)) {
    for (j in 1:4)
    x[j,i] <- as.numeric(x[[j,i]])
  }
}

to_num(sgobs38)
to_num(sgobs58)
to_num(sgobs68)
to_num(sgobs78)

countABC <- function(x) {
  ttcount <- numeric(ncol(x))
  for (i in 2:ncol(x)){
    ttcount[i] = as.numeric(x[[1,i]]) + as.numeric(x[[2,i]]) + as.numeric(x[[3,i]])
  }
  ttcount
}

# calculate chi-squares
# (0.9375*(sgobs78[[1,i]]+sgobs78[[2,i]]+sgobs78[[3,i]]))
# use the count data without NA
# chi-square test with background and introgression ana.

for(i in 2:ncol(sgobs38)) {
  sgobs38[5,i] <-((as.numeric(sgobs38[[1,i]])-(0.9375*countABC(sgobs38)[i]))^2) / (0.9375*countABC(sgobs38)[i]) +((as.numeric(sgobs38[[3,i]]) + as.numeric(sgobs38[[2,i]]) - (0.0625*countABC(sgobs38)[i]))^2) / (0.0625*countABC(sgobs38)[i])
}

for(i in 2:ncol(sgobs58)) {
  sgobs58[5,i] <-((as.numeric(sgobs58[[1,i]])-(0.9375*countABC(sgobs58)[i]))^2) / (0.9375*countABC(sgobs58)[i]) +((as.numeric(sgobs58[[3,i]]) + as.numeric(sgobs58[[2,i]]) - (0.0625*countABC(sgobs58)[i]))^2) / (0.0625*countABC(sgobs58)[i])
}

for(i in 2:ncol(sgobs68)) {
  sgobs68[5,i] <-((as.numeric(sgobs68[[1,i]])-(0.9375*countABC(sgobs68)[i]))^2) / (0.9375*countABC(sgobs68)[i]) +((as.numeric(sgobs68[[3,i]]) + as.numeric(sgobs68[[2,i]]) - (0.0625*countABC(sgobs68)[i]))^2) / (0.0625*countABC(sgobs68)[i])
}

for(i in 2:ncol(sgobs78)) {
  sgobs78[5,i] <-((as.numeric(sgobs78[[1,i]])-(0.9375*countABC(sgobs78)[i]))^2) / (0.9375*countABC(sgobs78)[i]) +((as.numeric(sgobs78[[3,i]]) + as.numeric(sgobs78[[2,i]]) - (0.0625*countABC(sgobs78)[i]))^2) / (0.0625*countABC(sgobs78)[i])
}

sgobs38[5,1] <- "chi-square"
sgobs58[5,1] <- "chi-square"
sgobs68[5,1] <- "chi-square"
sgobs78[5,1] <- "chi-square"


# calculate p-value given chi-squared and degrees of freedom
for (i in 2:ncol(sgobs38)){
  sgobs38[6,i] <- (pchisq(sgobs38[[5,i]],df=1, lower.tail = FALSE))
}

for (i in 2:ncol(sgobs58)){
  sgobs58[6,i] <- (pchisq(sgobs58[[5,i]],df=1, lower.tail = FALSE))
}

for (i in 2:ncol(sgobs68)){
  sgobs68[6,i] <- (pchisq(sgobs68[[5,i]],df=1, lower.tail = FALSE))
}

for (i in 2:ncol(sgobs78)){
  sgobs78[6,i] <- (pchisq(sgobs78[[5,i]],df=1, lower.tail = FALSE))
}

sgobs38[6,1] <- "P-value"
sgobs58[6,1] <- "P-value"
sgobs68[6,1] <- "P-value"
sgobs78[6,1] <- "P-value"

# calculate NA rate
for (i in 2:ncol(sgobs38)){
  sgobs38[7,i] <- (sgobs38[[4,i]]/(sgobs38[[1,i]]+sgobs38[[2,i]]+sgobs38[[3,i]]+sgobs38[[4,i]]))*100
}

for (i in 2:ncol(sgobs58)){
  sgobs58[7,i] <- (sgobs58[[4,i]]/(sgobs58[[1,i]]+sgobs58[[2,i]]+sgobs58[[3,i]]+sgobs58[[4,i]]))*100
}

for (i in 2:ncol(sgobs68)){
  sgobs68[7,i] <- (sgobs68[[4,i]]/(sgobs68[[1,i]]+sgobs68[[2,i]]+sgobs68[[3,i]]+sgobs68[[4,i]]))*100
}

for (i in 2:ncol(sgobs78)){
  sgobs78[7,i] <- (sgobs78[[4,i]]/(sgobs78[[1,i]]+sgobs78[[2,i]]+sgobs78[[3,i]]+sgobs78[[4,i]]))*100
}

sgobs38[7,1] <- "NA_rate"
sgobs58[7,1] <- "NA_rate"
sgobs68[7,1] <- "NA_rate"
sgobs78[7,1] <- "NA_rate"

## if the segregation are significantly diferent or not
## bonferroni correaltion 
for (i in 2:ncol(sgobs38)){
  if (sgobs38[[6,i]] < (0.05/(ncol(sgobs38)-1))){
    sgobs38[8,i] = "Distorted"} 
  else {
    sgobs38[8,i] = "OK"}
}

for (i in 2:ncol(sgobs58)){
  if (sgobs58[[6,i]] < (0.05/(ncol(sgobs58)-1))){
    sgobs58[8,i] = "Distorted"} 
  else {
    sgobs58[8,i] = "OK"}
}

for (i in 2:ncol(sgobs68)){
  if (sgobs68[[6,i]] < (0.05/(ncol(sgobs68)-1))){
    sgobs68[8,i] = "Distorted"} 
  else {
    sgobs68[8,i] = "OK"}
}

for (i in 2:ncol(sgobs78)){
  if (sgobs78[[6,i]] < (0.05/(ncol(sgobs78)-1))){
    sgobs78[8,i] = "Distorted"} 
  else {
    sgobs78[8,i] = "OK"}
}

sgobs38[8,1] <- "Distored?"
sgobs58[8,1] <- "Distored?"
sgobs68[8,1] <- "Distored?"
sgobs78[8,1] <- "Distored?"
```
# chi-square with marker expecetd less than 5 is not acceptable, look at AB and BB together


# write out the tales
```{r}

write.csv(sgobs38, "sgobs38_new.csv")
write.csv(sgobs58, "sgobs58_new.csv")
write.csv(sgobs68, "sgobs68_new.csv")
write.csv(sgobs78, "sgobs78_new.csv")
```


# add three standard deviation of the data
```{r}
# first count the total marker number

sgobs38[9,1] <- "TOTAL"
sgobs58[9,1] <- "TOTAL"
sgobs68[9,1] <- "TOTAL"
sgobs78[9,1] <- "TOTAL"

for (i in (2:ncol(sgobs38))){
  sgobs38[9,i] <- as.numeric(sgobs38[[1,i]]) + as.numeric(sgobs38[[2,i]]) + as.numeric(sgobs38[[3,i]])
}

for (i in (2:ncol(sgobs58))){
  sgobs58[9,i] <- as.numeric(sgobs58[[1,i]]) + as.numeric(sgobs58[[2,i]]) + as.numeric(sgobs58[[3,i]])
}

for (i in (2:ncol(sgobs68))){
  sgobs68[9,i] <- as.numeric(sgobs68[[1,i]]) + as.numeric(sgobs68[[2,i]]) + as.numeric(sgobs68[[3,i]])
}

for (i in (2:ncol(sgobs78))){
  sgobs78[9,i] <- as.numeric(sgobs78[[1,i]]) + as.numeric(sgobs78[[2,i]]) + as.numeric(sgobs78[[3,i]])
}

# now calcualte the heterozygous rate
sgobs38[10,1] <- "heteo_rate"
sgobs58[10,1] <- "heteo_rate"
sgobs68[10,1] <- "heteo_rate"
sgobs78[10,1] <- "heteo_rate"

for (i in (2:ncol(sgobs38))){
  sgobs38[10,i] <- as.numeric(sgobs38[2,i])/as.numeric(sgobs38[9,i])
}

for (i in (2:ncol(sgobs58))){
  sgobs58[10,i] <- as.numeric(sgobs58[2,i])/as.numeric(sgobs58[9,i])
}

for (i in (2:ncol(sgobs68))){
  sgobs68[10,i] <- as.numeric(sgobs68[2,i])/as.numeric(sgobs68[9,i])
}

for (i in (2:ncol(sgobs78))){
  sgobs78[10,i] <- as.numeric(sgobs78[2,i])/as.numeric(sgobs78[9,i])
}

# get the sd of the hetero_rate
sg38_hetero <- as.numeric(as.vector(sgobs38[10,2:ncol(sgobs38)])) 
sg58_hetero <- as.numeric(as.vector(sgobs58[10,2:ncol(sgobs58)])) 
sg68_hetero <- as.numeric(as.vector(sgobs68[10,2:ncol(sgobs68)])) 
sg78_hetero <- as.numeric(as.vector(sgobs78[10,2:ncol(sgobs78)])) 

hist(sg38_hetero)
hist(sg58_hetero)
hist(sg68_hetero)
hist(sg78_hetero)
# right tailed,not normal

sg38_sd <- sd(sg38_hetero) #[1] 0.01009183
sg58_sd <- sd(sg58_hetero) # [1] 0.01888883
sg68_sd <- sd(sg68_hetero) # [1] 0.009789817
sg78_sd <- sd(sg78_hetero) # [1] 0.009789817
hist(sg38_hetero)
```



# try to take the monomorphic markers out 
```{r}
poly38 <- sgobs38[,1]
poly58 <- sgobs58[,1]
poly68 <- sgobs68[,1]
poly78 <- sgobs78[,1]

for (i in 2:ncol(sgobs38)){
  if (sgobs38[[3,i]]!=0 & sgobs38[[8,i]]=="OK"){
    poly38 <- cbind(poly38, sgobs38[,i])
  }
} 
# 252 polymorphic markers (231 OK)

for (i in 2:ncol(sgobs58)){
  if (sgobs58[[3,i]]!=0 & sgobs58[[8,i]]=="OK"){
    poly58 <- cbind(poly58, sgobs58[,i])
  }
} 
# 230 polymorohic markers (147 OK)

for (i in 2:ncol(sgobs68)){
  if (sgobs68[[3,i]]!=0 & sgobs68[[8,i]]=="OK"){
    poly68 <- cbind(poly68, sgobs68[,i])
  }
} 
# 267 polymorphic markers (247 OK)

for (i in 2:ncol(sgobs78)){
  if (sgobs78[[3,i]]!=0 & sgobs78[[8,i]]=="OK"){
    poly78 <- cbind(poly78, sgobs78[,i])
  }
} 
# 249 polymorphic markers (238 OK)

###########################################
#########################################

poly38 <- sgobs38[,1]
poly58 <- sgobs58[,1]
poly68 <- sgobs68[,1]
poly78 <- sgobs78[,1]

for (i in 2:ncol(sgobs38)){
  if (sgobs38[[3,i]]!=0){
    poly38 <- cbind(poly38, sgobs38[,i])
  }
} 
# 252 polymorphic markers (231 OK)


for (i in 2:ncol(sgobs58)){
  if (sgobs58[[3,i]]!=0){
    poly58 <- cbind(poly58, sgobs58[,i])
  }
} 
# 230 polymorohic markers (147 OK)

for (i in 2:ncol(sgobs68)){
  if (sgobs68[[3,i]]!=0){
    poly68 <- cbind(poly68, sgobs68[,i])
  }
} 
# 267 polymorphic markers (247 OK)

for (i in 2:ncol(sgobs78)){
  if (sgobs78[[3,i]]!=0){
    poly78 <- cbind(poly78, sgobs78[,i])
  }
} 
# 249 polymorphic markers (238 OK)

```


```{r}
# look at the new marker distribution
hpoly38 <- as.numeric(as.vector(poly38[10,2:ncol(poly38)])) 
hpoly58 <- as.numeric(as.vector(poly58[10,2:ncol(poly58)])) 
hpoly68 <- as.numeric(as.vector(poly68[10,2:ncol(poly68)])) 
hpoly78 <- as.numeric(as.vector(poly78[10,2:ncol(poly78)])) 

hist(hpoly38)
hist(hpoly58)
hist(hpoly68)
hist(hpoly78)

# still heavily right-tailed
# try to log it, log not working
# how about boot-straping
```


```{r}
# standard the data see if easier to find cut off
library(caret)

standard38 <- preProcess(poly38, method= c("center", "scale", "YeoJohnson", "nzv"))
standard38.1 <- predict(standard, poly38)
hist(as.numeric(as.vector(standard38.1[10,2:ncol(standard38.1)])), main = "distribition DRIL38 heterozugous rate")

standard58 <- preProcess(poly58, method= c("center", "scale", "YeoJohnson", "nzv"))
standard58.1 <- predict(standard, poly58)
hist(as.numeric(as.vector(standard58.1[10,2:ncol(standard58.1)])), main = "distribition DRIL58 heterozugous rate")

standard68 <- preProcess(poly68, method= c("center", "scale", "YeoJohnson", "nzv"))
standard68.1 <- predict(standard, poly68)
hist(as.numeric(as.vector(standard68.1[10,2:ncol(standard68.1)])), main = "distribition DRIL68 heterozugous rate")

standard78 <- preProcess(poly78, method= c("center", "scale", "YeoJohnson", "nzv"))
standard78.1 <- predict(standard, poly78)
hist(as.numeric(as.vector(standard78.1[10,2:ncol(standard78.1)])), main = "distribition DRIL78 heterozugous rate")
```



# tranpose the dataframes and look from the line side
```{r}
poly38 <- sgobs38[,1]
poly58 <- sgobs58[,1]
poly68 <- sgobs68[,1]
poly78 <- sgobs78[,1]

for (i in 2:ncol(sgobs38)){
  if (sgobs38[[3,i]]!=0){
    poly38 <- cbind(poly38, sgobs38[,i])
  }
} 
# 252 polymorphic markers (231 OK)


for (i in 2:ncol(sgobs58)){
  if (sgobs58[[3,i]]!=0){
    poly58 <- cbind(poly58, sgobs58[,i])
  }
} 
# 230 polymorohic markers (147 OK)

for (i in 2:ncol(sgobs68)){
  if (sgobs68[[3,i]]!=0){
    poly68 <- cbind(poly68, sgobs68[,i])
  }
} 
# 267 polymorphic markers (247 OK)

for (i in 2:ncol(sgobs78)){
  if (sgobs78[[3,i]]!=0){
    poly78 <- cbind(poly78, sgobs78[,i])
  }
} 
# 249 polymorphic markers (238 OK)

### 
# transpose the dataframe to look from the line side
# we need to add line name here
tp38 <- t(poly38)
tp58 <- t(poly58)
tp68 <- t(poly68)
tp78 <- t(poly78)
```



# try the boot straping method
```{r}
library(boot)
# function to obatain the mean
Bmean <- function(data, indices){
  d <- data[indices] # allow boot to select sample
  return(mean(d))
}

# bootstraping with 1000 replications
results <- boot(data = hpoly38, statistic = Bmean, R=1000)
results
results <- boot(data = hpoly58, statistic = Bmean, R=1000)
results
results <- boot(data = hpoly68, statistic = Bmean, R=1000)
results
results <- boot(data = hpoly78, statistic = Bmean, R=1000)
results
plot(results)

boot.ci(results, type = c("norm", "basic", "perc","bca"))
```